### 2017-12-24 icde/revision/sec-model.tex

In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-3ex}
\end{figure}

@@

\vspace{-1ex}
\subsection{Ranking with Importance Assembling}
\label{subsec-ensemble}

@@

However, the resulting author citation graph to compute the prestige is typically too large to handle. Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information. Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

>>>>

In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.
%
\markedb{Before going into details, we would like to point out that although this work focuses on query independent ranking, it can also be used for query dependent ranking. Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}

@@

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the {\em logscale percentage of the number of citations of each year} \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-3ex}
\end{figure}

@@

\vspace{-1ex}
\stitle{Remarks}. 
\markedb{
The goal of our TWPageRank is to change the values, \ie importance, on nodes. One may wonder why not directly change node values. However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it. Finally, we set the weight of edges to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
}

\subsection{Ranking with Importance Assembling}
\label{subsec-ensemble}

@@

%However, the resulting author citation graph to compute the prestige is typically too large to handle. 
\markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches xxx on \magdata. Handing such a graph is computationally expensive. }
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information.
%
\markedb{
By this, our model is able to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters. As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by selecting quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$. }
%Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

### 2017-12-24 icde/revision/sec-related.tex

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}. Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}. Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.

>>>>

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}. 
%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. 
\markedb{Scholarly graph is a kind of temporal graphs [xx] and temporal information is a key factor for scholarly article ranking.}
There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}. Different from previous work, the Time-Weighted PageRank of this work \markedb{is inspired by the impacts of articles} and discriminately propagates scores in terms of \markedb{temporal statistics of citations}.
